\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref} % For hyperlinks
\geometry{top=2cm, bottom=2cm, left=2cm, right=2cm}


\signature{} % Laissez vide pour utiliser le flushleft
\address{SIRGHI Vladimir \\ 31 Rue Bois Gentil \\ 74600, Annecy \\ tel: +33.638.60.80.85} % Votre adresse
\date{\today} % Date

\begin{document}

\begin{letter}{VAT Group AG\\
Office in the Swiss canton of St. Gallen\\
Switzerland}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the “System Engineer” position at VAT Group AG, as advertised on your site. With a Master's degree in "Electronic of Embedded Systems and Telecommunications" and over seven years of experience in the semiconductor industry,

I am excited about the opportunity to contribute my extensive background in embedded software engineering to your innovative team.

In my current role as an "Embedded Software Engineer" at "STMicroelectronics", I have successfully developed firmwares for ARM Cortex-M targets and FPGA SOC prototypes. I have demonstrated my ability to solve complex technical challenges by leading verification activities and collaborating closely with cross-functional teams, including digital design and product management. My proactive approach allows me to identify customer requirements efficiently, translating them into technical solutions that align with market demands.

My experience extends to hands-on product testing and documentation, where I created comprehensive firmware design documents and conducted integration tests. This background positions me well to lead feasibility studies and actively participate in development projects as required by your team. Furthermore, my effective problem-solving skills and ability to thrive in an agile environment equip me to support product tests and optimize offerings to meet evolving market needs.

I also bring strong communication skills, fluency in English, and familiarity with collaborating with engineering teams. My previous responsibility for code reviews and collaborative meetings has honed my ability to deliver training for sales and application engineers, ensuring that all team members are well-informed about product features and specifications.

I am particularly drawn to VAT Group's commitment to innovation within the semiconductor industry and the opportunity to work in a collaborative environment that celebrates bold ideas. I am eager to contribute my expertise and creativity to drive technology initiatives and support the growth of cutting-edge vacuum valves and systems.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and enthusiasm can contribute to VAT Group's continued success. 

\begin{flushleft}
Sincerely, \\
Vladimir SIRGHI, \\
Embedded Software Engineer.
\end{flushleft}

\end{letter}
\end{document}


\end{letter}
\end{document}